### 2013-02-09 draft.tex
save

\documentclass[12pt,a4paper,oneside,titlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{textcase} 
\usepackage{tocloft}
\usepackage{lastpage}
\usepackage{graphicx}
\graphicspath{{images/}}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usetikzlibrary{shapes, arrows}
\usepackage[left=3.5cm,right=1cm,top=2cm,bottom=2cm]{geometry}
\author{Kostenko}
\setcounter{tocdepth}{3}%для глубины страницы содаржения
\renewcommand{\baselinestretch}{1.25}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}} % точки в содержании для секций
\bibliographystyle{unsrt}
\begin{document}
{
\thispagestyle{empty}
\newpage
\centering

\textbf{
National Research University Higher School of Economics\\
}
Faculty of Business Informatics\\
School of Software Engineering\\
Software Management Department

@@

\section*{Abstract}
{
%В данной статье описывается подход к обнаружению и подсчету транспортных средств на атодорогах.
%Он основан на дифференциальном методе вычисления оптического потока, предложенном Лукасом и Канаде.
%Отличие данного метода от других состоит в том, что нет необходимости подготавливать модель фона.
%Так же описываются достоинства и недостатки данного подхода.
}

@@

In this chapter we will state the set of requirements for the algorithm.
As a formality we will state several definitions first.
As any video is a sequence of frames, every moment in time we have one frame called the current frame.
If the current frame is defined as i, the previous frame will be defined as (i-1).
We will consider all the moving objects such as vehicles, trees, humans as the foreground.
Whether the object is considered as a moving one depends on the camera properties and the environment.
So we define moving objects as the ones that shift their position in the current frame, relatively to previous frame.
When the camera moves, or the object in its focus, it leads to the image changes.
The description of the movements which can be seen is called the optical flow.
There are several methods for calculating this flow.
Lucas and Kanade developed one of them, using differential approach.
It will be described later in this paper.
Now let us move to the problem statement.
One of the most important problems of video surveillance is identifying the object of interest and following its trajectory through the sequence of the following frames.
This problem can be partitioned into several sub-problems.
In the beginning it is necessary to find the objects of interest, which can also be called the foreground objects.
Finding these objects involves separation of the foreground from the background of the image.
As a result we get a binary map of the moving objects.
After that we need to separate vehicles from other moving objects such as trees or humans. 
For doing so we limit the area in which we will track movement.
%и назовем ее областью интереса
A good choice will be a well-observed part of a highway. 
Then we need to track the changes in objects of interest coordinates in the following frames.

@@

\begin{figure}[h]
  \center{\includegraphics[width=10cm]{1.jpg}}
  \vspace{-5ex}
  \caption{Pixel-by-pixel frame difference method.}
  \label{fig:pixel_by_pixel}
\end{figure}

@@

It is necessary to consider that the method of subtracting the previous frame from the current frame gives good response near the moving object border. 
However, inside the objects borders the response is NOT SO GOOD.
If the vehicle is relatively large, the probability of its recognition as an object of the foreground is LITTLE.

@@

The short-term model is the model which we get, after applying the steps stated above.
The long-term model is the pixel-by-pixel sum of N previous short-term foreground models, where N is a positive integer and more than 1.  
N is found empirically and depends on characteristics of the camera and the environment.

@@

	\caption{========}
	\label{ris:image1}
\end{figure}

@@

\begin{figure}[h]
\begin{minipage}[h]{0.49\linewidth}
\center{\includegraphics[width=0.2\linewidth]{four-svyaznost.png} \\ a)}
\end{minipage}
\hfill
\begin{minipage}[h]{0.49\linewidth}
\center{\includegraphics[width=0.2\linewidth]{eight-svyaznost.png} \\ b)}
\end{minipage}
\caption{(a) 4-connected, (b) 8-connected}
\label{ris:connections}
\end{figure}

In our approach the 8 connected way is used, because it gives a significant raise in precision.
There are generally known two methods of image marking: recursive and iterative.
The shortcomings of the recursive approach are the following:
\begin{enumerate}
  \item a great amount of memory is needed for it;
  \item it is rather slow, compared to the iterative method.
\end{enumerate}
The iterative method is an alternative to the recursive approach. It can be often met in literature by the name of: "Sequential scanning algorithm".
Let us present it in detailed steps:

\begin{enumerate}
  \item To be specific, we start processing the pixels of the image from the left-top corner, going from the top to the bottom and from the left to the right.
  \item While cycling through the pixels of the image we ignore the background pixels, and mark the current pixel with the color of the top-left neighbouring pixel.
\end{enumerate}

@@

\begin{figure}[h]
  \center{\includegraphics[width=0.3\linewidth]{abc_mask.jpg}}
  \caption{ABS-mask.}
  \label{fig:abc_mask}
\end{figure}

\begin{figure}[h]
  \center{\includegraphics[width=0.3\linewidth]{abc_all_cases.jpg}}
  \caption{5 cases of ABS-mask.}
  \label{fig:abc_all_cases}
\end{figure}

\begin{enumerate}
	\item Position 0, where all three components of the mask are not marked — in this case we simply skip the pixel.
	\item Position 1, where only the A element is marked — in this case we have found a new object which gets its own unique number.
	\item Position 2, where only the B element is marked — in this case we mark the current  A pixel with a number from B.
	\item Position 3, where only the C element is marked — in this case we mark the current  A pixel with a number from C.
	\item Position 4, here the B and C marks are connected and equivalent  and the A pixel can be marked with the number either from C or B. In some implementations the equivalency graph of such marks is created, with some explanations. We do not consider it necessary. We are going to do the following - in the case, where B is equal to C, we go back and mark all processed pixels marked as C with B. This process will be described in detail later in this paper. 
\end{enumerate}

@@

==============
%
%Понятно, что при таком порядке обхода у текущего рассматриваемого пикселя верхний и левый сосед уже должны быть размечены.
%
=============

@@

After obtaining the set of connected areas in the current frame (which are vehicles that we are looking for), we need to determine which of these objects are new, and which of them has already existed in the previous frames.
We will consider the position of the connected area as the coordinates of its center.
These coordinates are calculated as the average value of all the X and Y coordinates of the pixels, that this area contains.
Thus, the problem can be stated in the following way: we need to match the set of connected areas that we have on the current frame with the sets of areas we had on the previous frames, and initialize new areas as they appear.
Earlier we made several key assumptions.
One of them was that the vehicle in the current frame has only slightly moved in respect to itself in the previous frame.
So, if we store the positions of the connected areas centers we can find the closest center of an area in the current frame to a center on the previous frame, using the method suggested by Lucas and Kanade [CITATION NEEDED] ==========
The main idea of this method is to find the closest point to the given point by giving every point its weight.
A more detailed description of this algorithm can be found here: =======

Let us sum up our approach in an overall algorithm scheme:
\begin{enumerate}
	\item Translate the image from RGB to gray scale;
	\item Process the gray scale image with the Gaussian filter (this is done to eliminate noise);
	\item Subtract the previous image from the current one;
	\item Highlight the connected areas which are most likely to be the vehicles;
	\item Compare the current connected areas with the same areas in the previous frames with the use of Lucas Kanade approach, initializing the new areas as they appear;
	\item If such an area intersects an area that we are surveilling, add 1 to the counter.
\end{enumerate}

@@

In this paper we proposed another method for counting the amount of vehicles on a highway.
The key propositions we made are the following:
\begin{enumerate}
	\item the background model does not necessarily need to be stored at all times;
	\item the Lucas - Kanade method suits the task of vehicle counting really well. 
\end{enumerate}

\newpage
\section{Bibliography}
1) Real Time Vehicle Detection and Counting Method for Unsupervised Traffic Video on Highways
Mrs. P.M.Daigavane † and Dr. P.R.Bajaj ††,
S. D. College of Engineering, M.S., INDIA

>>>>

\documentclass[12pt,a4paper,oneside,titlepage]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{textcase} 
\usepackage{tocloft}
\usepackage{lastpage}
\usepackage{graphicx}

\usepackage[font=small,labelfont=bf,labelsep=space]{caption}
\captionsetup{%
  figurename=Fig.,
  tablename=tab.
}

\graphicspath{{images/}}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usetikzlibrary{shapes, arrows}
\usepackage[left=3.5cm,right=1cm,top=2cm,bottom=2cm]{geometry}
\author{Kostenko}
\setcounter{tocdepth}{3}%для глубины страницы содаржения
\renewcommand{\baselinestretch}{1.25}
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}} % точки в содержании для секций
\bibliographystyle{unsrt}
\begin{document}
{
\thispagestyle{empty}
\newpage
\centering

\textbf{
National Research University Higher School of Economics\\
}
Faculty of Business Informatics

School of Software Engineering

Software Management Department

@@

\section*{Abstract}
{
%В данной статье описывается подход к обнаружению и подсчету транспортных средств на атодорогах.
%Он основан на дифференциальном методе вычисления оптического потока, предложенном Лукасом и Канаде.
%Отличие данного метода от других состоит в том, что нет необходимости подготавливать модель фона.
%Так же описываются достоинства и недостатки данного подхода.

\cite{lucaskanade}
}

@@

In this chapter we will state the set of requirements for the algorithm.
As a formality we will state several definitions first.
As any video is a sequence of frames, every moment in time we have one frame called the current frame.
If the current frame is defined as i, the previous frame will be defined as (i-1).
We will consider all the moving objects such as vehicles, trees, humans as the foreground.
Whether the object is considered as a moving one depends on the camera properties and the environment.
So we define moving objects as the ones that shift their position in the current frame, relatively to previous frame.
When the camera moves, or the object in its focus, it leads to the image changes.
The description of the movements which can be seen is called the optical flow.
There are several methods for calculating this flow.
Lucas and Kanade developed one of them, using differential approach \cite{lucaskanade}.
It will be described later in this paper.
Now let us move to the problem statement.
One of the most important problems of video surveillance is identifying the object of interest and following its trajectory through the sequence of the following frames.
This problem can be partitioned into several sub-problems.
In the beginning it is necessary to find the objects of interest, which can also be called the foreground objects.
Finding these objects involves separation of the foreground from the background of the image.
As a result we get a binary map of the moving objects.
After that we need to separate vehicles from other moving objects such as trees or humans. 
For doing so we limit the area in which we will track movement.
%и назовем ее областью интереса
A good choice will be a well-observed part of a highway. 
Then we need to track the changes in objects of interest coordinates in the following frames.

@@

\begin{figure}[h]
  \center{\includegraphics[width=10cm]{1.jpg}}
  \vspace{-5ex}
  \caption{\textit{Pixel-by-pixel frame difference method.}}
  \label{fig:pixel_by_pixel}
\end{figure}

@@

It is necessary to consider that the method of subtracting the previous frame from the current frame gives good response near the moving object border. 
However, inside the objects borders the response is NOT SO GOOD.
If the vehicle is relatively large, the probability of its recognition as an object of the foreground is low.

@@

The short-term model is the model which we get, after applying the steps stated above.
The long-term model is the pixel-by-pixel sum of N previous short-term foreground models, where N is a positive integer and more than 1 (Fig.\ref{fig:frames_and_sum}).
N is found empirically and depends on characteristics of the camera and the environment.

@@

	\caption{\textit{(a) - first frame; (b) - secind frame; (c) - third frame; (d) - fourth frame; (e) - sum of all frames.}}
	\label{fig:frames_and_sum}
\end{figure}

@@

\begin{figure}[h]
\begin{minipage}[h]{0.49\linewidth}
\center{\includegraphics[width=0.2\linewidth]{four-svyaznost.png} \\ a)}
\end{minipage}
\hfill
\begin{minipage}[h]{0.49\linewidth}
\center{\includegraphics[width=0.2\linewidth]{eight-svyaznost.png} \\ b)}
\end{minipage}
\caption{\textit{(a) 4-connected, (b) 8-connected}}
\label{ris:connections}
\end{figure}

In our approach the 8 connected way is used, because it gives a significant raise in precision.
There are generally known two methods of image marking: recursive and iterative.
The shortcomings of the recursive approach are the following:
\begin{enumerate}
  \item a great amount of memory is needed for it;
  \item it is rather slow, compared to the iterative method.
\end{enumerate}
The iterative method is an alternative to the recursive approach. It can be often met in literature by the name of: "Sequential scanning algorithm".
Let us present it in detailed steps:
\begin{enumerate}
  \item To be specific, we start processing the pixels of the image from the left-top corner, going from the top to the bottom and from the left to the right.
  \item While cycling through the pixels of the image we ignore the background pixels, and mark the current pixel with the color of the top-left neighbouring pixel.
\end{enumerate}

@@

\begin{figure}[h]
  \center{\includegraphics[width=0.3\linewidth]{abc_mask.jpg}}
  \caption{\textit{ABC-mask.}}
  \label{fig:abc_mask}
\end{figure}

\begin{figure}[h]
  \center{\includegraphics[width=0.3\linewidth]{abc_all_cases.jpg}}
  \caption{\textit{5 cases of ABC-mask.}}
  \label{fig:abc_all_cases}
\end{figure}

\begin{enumerate}
	\item Position 0, where all three components of the mask are not marked — in this case we simply skip the pixel.
	\item Position 1, where only the A element is marked — in this case we have found a new object which gets its own unique number.
	\item Position 2, where only the B element is marked — in this case we mark the current  A pixel with a number from B.
	\item Position 3, where only the C element is marked — in this case we mark the current  A pixel with a number from C.
	\item Position 4, here the B and C marks are connected and equivalent  and the A pixel can be marked with the number either from C or B. In some implementations the equivalence graph of such marks is created, with some explanations. We do not consider it necessary. We are going to do the following - in the case, where B is equal to C, we go back and mark all processed pixels marked as C with B. This process will be described in detail later in this paper. 
\end{enumerate}

@@

===========
%
%Понятно, что при таком порядке обхода у текущего рассматриваемого пикселя верхний и левый сосед уже должны быть размечены.
%
=============

@@

After obtaining the set of connected areas in the current frame (which are vehicles that we are looking for), we need to determine which of these objects are new, and which of them has already existed in the previous frames.
We will consider the position of the connected area as the coordinates of its center.
These coordinates are calculated as the average value of all the X and Y coordinates of the pixels, that this area contains.
Thus, the problem can be stated in the following way: we need to match the set of connected areas that we have on the current frame with the sets of areas we had on the previous frames, and initialize new areas as they appear.
Earlier we made several key assumptions.
One of them was that the vehicle in the current frame has only slightly moved in respect to itself in the previous frame.
So, if we store the positions of the connected areas centres we can find the closest center of an area in the current frame to a center on the previous frame, using the method suggested by Lucas and Kanade \cite{lucaskanade}.
The main idea of this method is to find the closest point to the given point by giving every point its weight.
A more detailed description of this algorithm can be found here: \cite{lucaskanade}.

Let us sum up our approach in an overall algorithm scheme:
\begin{enumerate}
	\item Translate the image from RGB to gray scale;
	\item Process the gray scale image with the Gaussian filter (this is done to eliminate noise);
	\item Subtract the previous image from the current one;
	\item Highlight the connected areas which are most likely to be the vehicles;
	\item Compare the current connected areas with the same areas in the previous frames with the use of Lucas Kanade approach \cite{lucaskanade}, initializing the new areas as they appear;
	\item If such an area intersects an area that we are surveilling, add 1 to the counter.
\end{enumerate}

In this paper we proposed another method for counting the amount of vehicles on a highway.
The key propositions we made are the following:
\begin{enumerate}
	\item the background model does not necessarily need to be stored at all times;
	\item the Lucas - Kanade method \cite{lucaskanade} suits the task of vehicle counting really well. 
\end{enumerate}

\newpage
\section{Bibliography}
\begin{thebibliography}{99}
\bibitem{lucaskanade} An Iterative Image Registration Technique with an Application to Stereo Vision, Bruce D. Lucas Takeo Kanade, Computer Science Department Carnegie-Mellon University Pittsburgh, Pennsylvania 15213

\bibitem{realtime_vehicle_detection} Real Time Vehicle Detection and Counting Method for Unsupervised Traffic Video on Highways, Mrs. P.M.Daigavane † and Dr. P.R.Bajaj ††, S. D. College of Engineering, M.S., INDIA
\end{thebibliography}

\newpage
\section{Appendix}

@@
